R Notebook

### 2022-01-31 Code/Simulation.Rmd
Added block bootstrap, working incorrectly

>>>>

```{r}
# Split sample size into blocks, apply bootstrap onto blocks. Use that as x.b. Fit, stat.b
nmblk <- function(n, l) {
    b <- n / l
    idx <- sample(seq(1, n - l + 1, by = l), b, replace = TRUE)
    c(outer(0:(l - 1), idx, "+"))
}

mvblk <- function(n, l) {
    b <- n / l
    idx <- sample(1:(n - l + 1), b, replace = TRUE)
    c(outer(0:(l - 1), idx, "+"))
}

test_block <- function(ar, B = 1000, l, n) {

  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
  stat <- ks.test(x, "pnorm")$statistic
  stat.b <- double(B)
  for (i in 1:B) {
    x.b <- x[nmblk(n, l)]
    stat.b[i] <- ks.test(x.b, "pnorm")$statistic
  }

  p.value <- (sum(stat.b >= stat)) / (B + 1)
  list(p.value = p.value)
}

# Naive KS-test to show consequence of fitted parameters
test_naive_block <- function(ar, n) {
  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
  p.value <- ks.test(x, "pnorm")$p.value
  list(p.value = p.value)
}

# Generate results
pvals_block <- suppressWarnings(replicate(20, test_block(ar = 0.5, B = 1000, l = 5, n = 100)$p.value))
pvals_block
pvals_naive_block <- suppressWarnings(replicate(20, test_naive_block(ar = 0.5, n = 100)$p.value))

# Create a master data_frame with all the results
histogram <- c(rep("Block", 20), rep("Naive", 20))
p_values <- c(pvals_block, pvals_naive_block)
results <- data_frame(p_values, histogram)

# Generate histograms plot
hist_boot <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~histogram, scales = "free_y")
hist_boot
```

```{r}
# Split sample size into blocks, apply bootstrap onto blocks. Use that as x.b. Fit, stat.b
# Test parametric bootstrap as a solution to fitting parameters
test_corr_block <- function(ar, B = 1000, l, n) {

  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)

  # Store KS statistic from using fitted parameters
  stat <- cor(x[-1], x[-length(x)])

  # Parametric bootstrap to approximate the null distribution
  stat.b <- double(B)
  for (i in 1:B) {
    x.b <- x[nmblk(n, l)]
    stat.b[i] <- cor(x.b[-1], x.b[-length(x.b)])
  }

  list(stat = stat, stat.b = stat.b)
}

do1rep <- function(ar, B = 1000, l, n) {
    bt <- test_corr_block(ar, B, l, n)
    c(bt$stat, sd(bt$stat.b))
}

corr_block <- suppressWarnings(replicate(50, do1rep(0.5, B = 1000, 10, 100)))
corr_block
```
